Exploratory data analysis

### 2020-12-26 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

pca_vi <- DataExplorer::plot_prcomp(vi_data_corrected_buffer2_no_defol_no_response,
  variance_cap = 0.90,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 3),
  parallel = TRUE
)
pca_vi = pca_vi[[1]] +
  labs(title = "Target POV: 90%")
pca_vi
```

@@

pca_nri <- DataExplorer::plot_prcomp(nri_data_corrected_buffer2_no_response,
  variance_cap = 0.9,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 3),
  parallel = TRUE
)
pca_nri = pca_nri[[1]] + 
  labs(title = "Target POV: 90%")
pca_nri
```

@@

pca_hr <- DataExplorer::plot_prcomp(bands_data_corrected_buffer2_no_response,
  variance_cap = 0.98,
  geom_label_args = list(size = 3),
  ggtheme = ggpubr::theme_pubclean()
)
pca_hr = pca_hr[[1]] + 
  labs(title = "Target POV: 90%")
pca_hr
```

>>>>

pca_vi <- DataExplorer::plot_prcomp(vi_data_corrected_buffer2_no_defol_no_response,
  variance_cap = 0.90,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 1),
  parallel = TRUE
)
pca_vi = pca_vi[[1]] +
  labs(title = "Target POV: 90%")
pca_vi
```

@@

pca_nri <- DataExplorer::plot_prcomp(nri_data_corrected_buffer2_no_response,
  variance_cap = 0.9,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 1),
  parallel = TRUE
)
pca_nri = pca_nri[[1]] + 
  labs(title = "Target POV: 90%")
pca_nri
```

@@

pca_hr <- DataExplorer::plot_prcomp(bands_data_corrected_buffer2_no_response,
  variance_cap = 0.98,
  geom_label_args = list(size = 1),
  ggtheme = ggpubr::theme_pubclean()
)
pca_hr = pca_hr[[1]] + 
  labs(title = "Target POV: 90%")
pca_hr
```
